Results

### 2023-03-28 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
I knew tables in markdown were trouble when i walked in

To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVA comparing subjective arousal, *Corrugator* and *Levator* activity of four strategies (active viewing, distraction, distancing, suppression). 
We found a significant effect of strategy for subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.
For detailed information on post-hoc tests, please see tables \@ref(tab:SupplEffectArousalReg) to \@ref(tab:SupplEffectLevReg) and figures \@ref(fig:SupplFigArousalReg) to \@ref(fig:SupplFigLevReg) in the [supplementary material](#SupplementEffectER).
[INSERT TABLE 1 HERE]

``` {r TabDescr, echo=FALSE, message=FALSE, warning=FALSE}
papaja::apa_table(
  df.descr,
  caption = "$M \\pm SD$ of subjective arousal, subjetive effort, subjective utility, Corrugator activity, and Levator activity for each condition.",
  escape = FALSE,
  placement = "H",
  landscape = TRUE)
```

>>>>

To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVA comparing subjective arousal, *Corrugator* and *Levator* activity of four strategies (active viewing, distraction, distancing, suppression). 
We found a significant effect of strategy for subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.
For detailed information on post-hoc tests, please see tables \@ref(tab:SupplEffectArousalReg) to \@ref(tab:SupplEffectLevReg) and figures \@ref(fig:SupplFigArousalReg) to \@ref(fig:SupplFigLevReg) in the [supplementary material](#SupplementEffectER).

[INSERT TABLE 1 HERE]

``` {r TabDescr, echo=FALSE, message=FALSE, warning=FALSE}
papaja::apa_table(
  df.descr,
  caption = "$M \\pm SD$ of subjective arousal, subjetive effort, subjective utility, Corrugator activity, and Levator activity for each condition.",
  escape = FALSE,
  placement = "H",
  align = c("r","c","c","c","c","c"),
  landscape = TRUE)
```
